The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-30 manuscript/manuscript.Rnw
discuss fusion proteins more completely

While Syncytin-1 and -2 are implicated in the formation of the
syncytiotrophoblast in
\human~\cite{Rawn.ea2008:evolutionregulationandfunction} and homologs
of \ac{ERVFRD-1} and \ac{ERVW-1} are widely expressed in most
of the placentas analyzed here, they are not expressed in \bonobo,
\sheep, and \dog, even though these mammals form
syncytiotrophoblasts~\cite{Mess.ea2006:Evolutionarytransformationsoffetal}.
Because the formation of syncytiotrophoblast is the stem state of
Eutheria, Afrotheria, Euarchontoglires, and
Laurasiatheria~\cite{Mess.ea2006:Evolutionarytransformationsoffetal},
the gene(s) responsible for cytotrophoblast fusion to form
syncytiotrophoblast is likely to be highly expressed in the core
placenta. \ac{ANXA5} is known to be expressed at multiple stages
of placentation, and is capable of repairing membrane defects and
promoting the fusion of
cells~\cite{Carmeille.ea2015:Annexin-A5promotesmembraneresealing} in
the presence of Ca$^{2+}$. While there are likely other genes which
are responsible for the positioning of cytotrophoblast cells in close
proximity to start the fusion process, we hypothesize that \ac{ANXA5} is
essential for the completion of fusion and the maintenance of membrane
repair during the massive flux of nutrients and waste in the placenta.

@@

>>>>

While Syncytin-1 and -2 (\ac{ERVW-1} and \ac{ERVFRD-1}, respectively) are implicated
in the formation of the syncytiotrophoblast in
\human~\cite{Rawn.ea2008:evolutionregulationandfunction} and homologs
of \ac{ERVFRD-1} and \ac{ERVW-1} are widely expressed in most of the
placentas analyzed here, they are not expressed in \bonobo, \sheep,
and \dog, even though these mammals form
syncytiotrophoblasts~\cite{Mess.ea2006:Evolutionarytransformationsoffetal}.
Because the formation of syncytiotrophoblast is the stem state of
Eutheria, Afrotheria, Euarchontoglires, and
Laurasiatheria~\cite{Mess.ea2006:Evolutionarytransformationsoffetal},
and syncytiotrophoblast must be continuously replenished
the gene(s) responsible for cytotrophoblast fusion to form
syncytiotrophoblast should be highly expressed in the core
placenta. \ac{ANXA5} is known to be expressed at multiple stages of
placentation, and is capable of repairing membrane defects and
promoting the fusion of
cells~\cite{Carmeille.ea2015:Annexin-A5promotesmembraneresealing} in
the presence of Ca$^{2+}$. While there may be other genes which
are responsible for the positioning of cytotrophoblast cells in close
proximity to start the fusion process, \ac{ANXA5} is likely to
be essential for the completion of fusion and the maintenance of
membrane repair during the massive flux of nutrients and waste in the
placenta \cite{Carmeille.ea2015:Annexin-A5promotesmembraneresealing,Ueki.ea2012:Lossofmaternalannexin}.

@@

\DLA{Added the Carmeille.ea2015 and Ueki.ea2012 I have other
  references
  (\cite{Ota.ea2013:ContributionoffetalANXA5,Bouter.ea2015:ReviewAnnexin-A5andcell})
  but I'd exceed the limit for placenta (45)}
